Assessing Virulence by MCG

### 2017-09-07 doc/RMD/MCG-virulence.Rmd
Add test for assessor

```{r load_data}
datcols <- cols(
  .default = col_integer(),
  Severity = col_double(),
  Region = col_character(),
  Source = col_character(),
  Host = col_character()
)
dat <- read_csv(file.path(PROJHOME, "data", "clean_data.csv"), col_types = datcols) %>%
  select(Severity, MCG, Region, Source)
dat
```

@@

## Visualizing distributions

@@

>>>>

```{r load_data}
datcols <- cols(
  .default = col_integer(),
  Severity = col_double(),
  Region = col_character(),
  Source = col_character(),
  Host = col_character()
)
dat <- read_csv(file.path(PROJHOME, "data", "clean_data.csv"), col_types = datcols) %>%
  select(Severity, MCG, Region, Source, Year)
dat
```

@@

# Assessing virulence by MCG

@@

## Testing for differences by assessor

The straw test, until the end of 2007, was performed by Lindsey Otto-Hanson. 
After that, these were performed by Serena McCoy. The Steadman lab was careful
to train their members consistently in these practices, so the results from this
test should be equivalent, but we want to ensure that there are no hidden biases
between the two. To do this, we will test for differences within region.

```{r assessor-diff}
set.seed(2017-06-29)
assessor_dat <- dat %>%
  group_by(Region, Year) %>%
  filter(n() > 5) %>%
  mutate(mean_sev = mean(Severity)) %>%
  mutate(Source = ifelse(Source == "wmn", "wmn", "producer field")) %>%
  arrange(desc(mean_sev)) %>%
  ungroup() %>%
  mutate(Region = forcats::fct_inorder(Region)) %>%
  mutate(Assessor = factor(ifelse(Year <= 2007, "Otto-Hanson", "McCoy"))) %>% 
  select(Region, Assessor, Severity, Source)
res <- aov(Severity ~ Region + Assessor, data = assessor_dat)
res
summary(res)
```

# Assessing virulence by multilocus genotype
